Towards Practical First-Order Model Counting

### 2025-01-31 doc/paper/paper.tex
Funding

\author{Ananth K. Kidambi}{Indian Institute of Technology Bombay, Mumbai, India}{210051002@iitb.ac.in}{}{TODO: funding}
\author{Guramrit Singh}{Indian Institute of Technology Bombay, Mumbai, India}{guramrit@iitb.ac.in}{}{TODO: funding}
\author{Paulius Dilkas}{University of Toronto, Toronto, Canada \and Vector Institute, Toronto, Canada \and \url{https://dilkas.github.io/}}{paulius.dilkas@utoronto.ca}{https://orcid.org/0000-0001-9185-7840}{TODO: funding}
\author{Kuldeep S. Meel}{University of Toronto, Toronto, Canada \and \url{https://www.cs.toronto.edu/~meel/}}{meel@cs.toronto.edu}{https://orcid.org/0000-0001-9423-5270}{TODO: funding}

@@

%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.

\acknowledgements{Part of the research was conducted while all authors were at the National University of Singapore.}

@@

\todo[inline,caption={}]{
  For the entire paper:
  \begin{itemize}
    \item Perhaps I can list the `authors contributed equally' statement as part
          of Funding. Check K's recent papers.
    \item Sentence vs formula: be consistent and not confusing
    \item 15 pages excluding references
    \item Go through the rest of formatting instructions (in GTD)
    \item Make sure all the internal references (e.g., to examples) are still
          valid
    \item Maybe add extra references to subsections
  \end{itemize}
}
\section{Introduction}

>>>>

\author{Ananth K. Kidambi}{Indian Institute of Technology Bombay, Mumbai, India}{210051002@iitb.ac.in}{}{}
\author{Guramrit Singh}{Indian Institute of Technology Bombay, Mumbai, India}{guramrit@iitb.ac.in}{}{}
\author{Paulius Dilkas}{University of Toronto, Toronto, Canada \and Vector Institute, Toronto, Canada \and \url{https://dilkas.github.io/}}{paulius.dilkas@utoronto.ca}{https://orcid.org/0000-0001-9185-7840}{}
\author{Kuldeep S. Meel}{University of Toronto, Toronto, Canada \and \url{https://www.cs.toronto.edu/~meel/}}{meel@cs.toronto.edu}{https://orcid.org/0000-0001-9423-5270}{}

@@

\funding{This research was funded in part by the Natural Sciences and
  Engineering Research Council of Canada (NSERC), funding reference number
  RGPIN-2024-05956, and the Digital Research Alliance of Canada
  (\texttt{\href{https://alliancecan.ca/}{alliancecan.ca}}).}

\acknowledgements{The first two authors contributed equally. Part of the
  research was conducted while all authors were at the National University of
  Singapore.}

@@

\todo[inline,caption={}]{
  For the entire paper:
  \begin{itemize}
    \item Sentence vs formula: be consistent and not confusing
    \item 15 pages excluding references
    \item Make sure all the internal references (e.g., to examples) are still
          valid
    \item Maybe add extra references to subsections
    \item When submitting: go through the rest of formatting instructions (in
          GTD)
  \end{itemize}
}
\section{Introduction}
